\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Harish Gowda R} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 7760471879 \\ Bengaluru, INDIA} 
\address{\href{mailto:harishhgowdaa@gmail.com}{harishharishgowda42@gmail.com} \\ \href{https://linkedin.com/in/harishhgowda}{LinkedIn Profile} \\ \href{https://github.com/harishhgowda}{Github Profile}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

%\begin{rSection}{SUMMARY}

%{Software Engineer specializing in Artificial Intelligence, Machine Learning and Full-Stack development. Experienced in Python, JAVA, HTML, CSS, SQL, and various frameworks. Completed internships in Artificial Intelligence and Data Science, with real-time project experience. Strong problem-solving skills with leadership experience. Committed to staying current with the latest techniques and technologies in the field.}


%\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Technology in Computer Science and Engineering [B-Tech, Graduation]}\hfill {2021 - 2025}\\
Nagarjuna College of Engineering and Technology, Bengaluru\hfill {GPA: 7.5}

{\bf Physics, Chemistry, Maths, Computer Science [PCMC, Intermediate]}\hfill {2019 - 2021}\\
St.Theresa Mahesh Pre-University College, Bengaluru \hfill GPA: 78.6

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{TECHNICAL SKILLS AND INTERESTS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & C, C++, Python, JAVA, SQL, MongoDB, XML, Javascript, HTML + CSS.
\\
Libraries & TensorFlow, NumPy, PyTorch, Keras, Pandas, Scikit-learn, JavaScript, Seaborn,\\& OpenCV, Python Libraries, ReactJs.\\
Web Dev Tools &  Nodejs, VScode, Git, Github, Bootstrap, Angular, React, Sketch.\\
Frameworks &  ReactJs, Spring, Node, Angular, Flask.\\
Cloud/Databases & MongoDb, Firebase, Relational Database(mySql).\\
Relevent Coursework &  Data Structures and Algorithms, Operating Systems, Object Oriented Programming,\\ & Database Management System, Software Engineering.\\
Area of Interests &    Artificial Intelligence and Machine Learning Development, Software Engineer, \\ &Web Dev, Cloud Security.\\
Soft Skills &  Self and Continuous-learning, Presentation, Creativity, Emotional Intelligence.
\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{INTERN} \hfill June 2023 - June 2025\\
NxtWave CCBP 4.0 Academy\hfill \textit{Bengaluru, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Engineered a comprehensive Java Full Stack solution, integrating JAVA, React JS, and Spring, which increased system efficiency by 30\%.
     \item Enhanced website performance by optimizing HTML and CSS code, resulting in a 40\% increase in page loading speed and a 25\% decrease in bounce rate.
    \item Spearheaded the creation of responsive web designs with Bootstrap, improving mobile user experience by 30\% and boosting conversion rates by 20\%.
\\ &
 \end{itemize}


\textbf{INTERN On-campus} \hfill December 2022 - February 2023\\
Technical Hub \hfill \textit{Bengaluru, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item  Achieved proficiency in Python Programming, from fundamental concepts to advanced applications, resulting in a 50\% reduction in code execution time.
     \item  Identified and assessed the critical role of Python in industry-level applications, leading to a 20\% increase in operational efficiency.
     \\ &
 \end{itemize}

 \textbf{Artifical Intelligence INTERN} \hfill October 2023 - November 2023\\
 CodSoft \hfill \textit{Bengaluru, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Resolved complex problems within the scope of Artificial Intelligence, improving model accuracy by 25\%
     \item  Expanded expertise in Python’s application in Data Science and statistical foundations, enhancing data processing speed by 40\%.
     \\ &
     \\ &
 \end{itemize}

 \textbf{Data Science INTERN} \hfill November 2023 - December 2023\\
 TechnoHacks EduTech \hfill \textit{Bengaluru, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Executed comprehensive assignments demonstrating proficiency in Data Science methodologies, increasing project completion rate by 30\%.
     \item Pioneering Machine Learning models utilizing SVM algorithms for spam email filtering, weather data analysis, and fraud transaction detection, reducing false positives by 15\%.
 \end{itemize}

\end{rSection} 



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{ Amazon Product Reviews Sentiment Analysis.} 
    \begin{itemize}
    \item  Analyzed consumer reviews posted in real time on product pages using Python libraries such as numpy and math to extract actionable insights; guided product development decisions resulting in a 15\% increase in customer satisfaction. Technology Used: matplotlib, pandas, numpy, seaborn, math, Python. \href{https://hig-search.careerflow.ai/}{}
     \end{itemize}
\item \textbf{ Bitcoin Price Prediction.}
    \begin{itemize}
    \item { Devised a Bitcoin Price Prediction model using Machine Learning. This Data Science project increased prediction accuracy by 20\% using Support Vector Machines (Regression) and technologies such as Python, pandas, and numpy.}
    \end{itemize}
\item \textbf{ Malicious Email Investigation.}
    \begin{itemize}
    \item { Conducted a project on Malicious Email Investigation using Maltego, improving threat detection by 30\%. Built a custom OSINT Toolkit and configured Spiderfoot. Technologies used involve Kali Linux, Spiderfoot, and Maltego.}
    \end{itemize}
\item \textbf{ Covid-19 Cases Predictions.}
    \begin{itemize}
    \item { Developed a Machine Learning project for Covid-19 Cases Predictions, enhancing prediction accuracy by 25\%. Provided daily and weekly updated statistics tracking the number of COVID-19 cases, recoveries, and deaths. Technologies used included Python, pandas, numpy, matplotlib, and plotly.}
    \end{itemize}
\item \textbf{ AI Chatbot.}
    \begin{itemize}
    \item { Created an AI Chatbot using ML, DL, and Python, improving user interaction by 35\%. The chatbot was designed to understand the ‘intention’ behind every user message. Technologies used contain tensorflow, nltk, colorama, numpy, scikit-learn, Flask, and Python.}
    \end{itemize}
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
    \item 	Treasurer in Freshers Event \href{https://wapth.com/blog/}{}\href{https://wangpath}{}\href{https://w/fpath/?hl=en}{}helped to attract close to 300 attendees through communication Skills and Customer Service skills for this event. Collected over Rs. 75,000 in entry fees for different activities 
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership} 
\begin{itemize}
    \item Achieved the rank of Corporal in the National Cadet Corps (NCC), \href{https://diord.com/invite/WWbjEaZ}{} leading a team of 20 cadets. This experience helped to develop key qualities such as leadership, honesty, teamwork, and responsibility.
\end{itemize}


\end{rSection}


\end{document}